Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-06 algos/dynamic-limits.tex
Revert "did not compile fix"
This reverts commit 16ffa8b68cec7b644034fba24aca885a59e4db59.

git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@868 df1a90cd-247b-4364-bdaf-287a704eb499

It should be noted that while in the description of the dynamic limits algorithm we used notions of ``outgoing'' and ``incoming'' interfaces, in the real system all interfaces can be both incoming and outgoing.
Thus, it may not be entirely clear which outgoing limit $L_{of}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{if}$.
To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L'_{{if}^{FIB}}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{{of}^{FIB}}}$.

>>>>

It should be noted that while in the description of the dynamic limits algorithm we used notions of ``outgoing'' and ``incoming'' interfaces, in the real system all interfaces can be both incoming and outgoing.
Thus, it may not be entirely clear which outgoing limit $L_{of}$ (line 10 in the algorithm) should be used to calculate the incoming limit $L_{if}$.
To overcome this problem, in our actual implementation we enforced separate incoming/outgoing interface limits for each individual FIB entry.
That is, for each FIB entry we set a separate Interest limit for each incoming interface ($L'_{if}^{FIB}$) based on a sum of FIB entry limits for each outgoing interface $L=\sum{L_{of}^{FIB}}$.
